\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}

\titleformat{\subsection}
{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\setlist[itemize]{label=--}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=black,
}

\begin{document}

\pagestyle{empty}

\begin{center}
    {\Huge \textbf{Felipe Canton Públio}} \\
    \vspace{4mm}
    \href{https://www.publio.dev}{www.publio.dev} | \href{https://www.linkedin.com/in/felipe-publio}{www.linkedin.com/in/felipe-publio} \\
    \vspace{2mm}
    \href{mailto:felipe@publio.dev}{felipe@publio.dev} | São Paulo, Brazil
\end{center}
\hrule % Horizontal line separating the header

\section*{About}
Seasoned Software Engineer proficient in Java and Golang, specializing in backend development. Expert in Spring Boot, MVC, Batch, Cloud (AWS), Kafka, RabbitMQ, SQL, NoSQL, and Microservices architecture. Skilled in Terraform for Infrastructure as Code (IaC). Proven track record in optimizing system performance and scalability.

\section*{Experience}

\subsection*{Itaú Unibanco, Remote - Software Developer}
\subsubsection*{Since 2022/09}
\begin{itemize}
    \item Participated in the RedHat Linux homologation process, creating internal manuals and validating edge cases.
    \item Implemented AWS Pipelines with GitHub Actions, developed documentation for internal processes, and ensured efficient integration.
    \item Promoted Golang adoption in the CashManagement community, collaborated proactively, created documentation, and delivered presentations.
\end{itemize}

\subsection*{AB-Inbev (BEES), Remote - Software Developer}
\subsubsection*{2021/09 - 2022/09}
\begin{itemize}
    \item Designed and implemented a resilient and scalable data ingestion system for critical e-commerce applications using Java 11, Spring Boot, and Microservices.
    \item Managed monthly ingestion of billions of items with a focus on data accuracy and integrity.
    \item Utilized Kafka topics for efficient processing of vast event streams and led a team in designing and implementing a comprehensive monitoring platform.
\end{itemize}

\subsection*{Itaú Unibanco, Remote - Software Developer}
\subsubsection*{2021/06 - 2021/09}
\begin{itemize}
    \item Led the integration of Java, Kafka, AWS, and Cassandra technologies, ensuring seamless and efficient system operations.
    \item Played a pivotal role in the transformation of the Checking Account Balance API, implementing modern design patterns and enhancing code quality through rigorous refactoring.
    \item Managed a staggering volume of 1.2 billion monthly requests for the Checking Account Balance API, showcasing a robust and scalable system capable of meeting high-demand scenarios.
\end{itemize}

\subsection*{Busque Seguro, Remote - Software Developer}
\subsubsection*{2020/02 - 2021/06}
\begin{itemize}
    \item Led the project and constructed the insurance contracting system, designing a comprehensive comparison tool for various insurance providers.
    \item Implemented robust features for users to seamlessly navigate and compare offerings from different insurers.
    \item Participated actively in the project and construction of a system providing insurance for hotel guests, ensuring a seamless process for hotel guests to access and secure insurance.
\end{itemize}

\subsection*{Iteris Consultoria, Barueri - Jr. Software Developer}
\subsubsection*{2019/11 - 2021/03}
\begin{itemize}
    \item Utilized Spring Boot and Batch frameworks for microservices architecture, managing data with Oracle SQL.
    \item Architected microservices and optimized batch processes, enhancing system performance.
    \item Engineered seamless integration of financial services and bank loans, collaborating with Brazil's largest state bank.
\end{itemize}

\subsection*{Valemobi, São Paulo - Software Developer (Intern)}
\subsubsection*{2019/08 - 2019/11}
\begin{itemize}
    \item Worked on Java/Kotlin back-end and Coldfusion, AngularJS front-end for an insurance comparison platform.
\end{itemize}

\subsection*{Optum (United Health Group), São Paulo - Software Developer (Intern)}
\subsubsection*{2018/10 - 2019/08}
\begin{itemize}
    \item Worked on Java/Spring Boot/MVC for dashboards development in Tableau.
\end{itemize}

\section*{Education}

\begin{itemize}
    \item \textbf{Universidade Anhembi Morumbi, São Paulo} - Analysis and Systems Development (2018 - 2020)
    \item \textbf{Escola Técnica Estadual, São Paulo} - Electronics (2014 - 2016)
\end{itemize}

\section*{Certifications}
\begin{itemize}
    \item \textbf{Caelum, São Paulo - SP} - Microservices with Spring Cloud - FJ-33
\end{itemize}

\section*{Projects}
\begin{itemize}
    \item \textbf{YouTube Channel} - Disseminate knowledge about software development in Portuguese
\end{itemize}

\section*{Languages}
\begin{itemize}
    \item Brazilian Portuguese - Native
    \item English - Advanced
\end{itemize}

\end{document}
